quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays

### 2025-01-13 man/manuscript/manuscript.qmd
Update manuscript

---
title: "quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays"
author:
    - name: 
        given: Gage
        family: Rowden
        id: GR
        orcid: 0000-0002-7517-0480
        email: rowde002@umn.edu
        affiliation:
          name: University of Minnesota
          city: Saint Paul
          state: MN
        roles:
          Conceptualization
          Methodology
          Software
          Validation
          Formal analysis
          Investigation
          Resources
          Data curation
          Writing--original draft preparation
          Writing--review and editing
          Visualization
          Supervision
          Prject administration
        corresponding: true
    - name:
        given: Peter
        family: Larsen
        id: PL
        orcid: 0000-0000-0000-0000
        email: plarsen@umn.edu
        affiliation:
          name: University of Minnesota
          city: Saint Paul
          state: MN
        roles:
          Supervision
          Project administration
          Funding

abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is still relatively new, academic and industry standards for cleaning data and analyzing results have yet to be fully established. The open source R library, quicR, was developed to fill this lack of standardization. This library provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualiztion.
keywords: quicR, R, library, RT-QuIC, prion, diagnostics, CJD, Parkinson's
format: 
  pdf:
    papersize: letter
    documentclass: article
    fontsize: 12pt
    geometry:
      - top=20mm
      - right=20mm
      - bottom=20mm
      - left=20mm
    fig-pos: "H"
    include-in-header: 
      - text: \usepackage{tabularray}
      - text: \usepackage{float}
      - text: \floatplacement{table}{H}
mainfont: Calibri
bibliography: references.bib
bibliographystyle: apa
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(quicR)
library(dplyr)
library(tidyr)
library(kableExtra)
library(readxl)
library(readr)
library(ggplot2)
library(reshape2)

>>>>

---
title: "quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays"
authors:
    - id: GR
      name: Gage Rowden
      orcid: 0000-0002-7517-0480
      email: rowde002@umn.edu
      affiliations:
        - name: University of Minnesota
          city: Saint Paul
          state: MN
        - name: Priogen Corp.
          city: Saint Paul
          state: MN
      roles:
          Conceptualization
          Methodology
          Software
          Validation
          Formal analysis
          Investigation
          Resources
          Data curation
          Writing--original draft preparation
          Writing--review and editing
          Visualization
          Supervision
          Prject administration
      corresponding: true
    - id: PL
      name: Peter Larsen
      orcid: 0000-0002-3634-3625
      email: plarsen@umn.edu
      affiliations:
        - name: University of Minnesota
          city: Saint Paul
          state: MN
        - name: Priogen Corp.
          city: Saint Paul
          state: MN
      roles:
          Supervision
          Project administration
          Funding

abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is still relatively new, academic and industry standards for cleaning data and analyzing results have yet to be fully established. The open source R library, quicR, was developed to fill this lack of standardization. This library provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualiztion.
keywords: quicR, R, library, RT-QuIC, prion, diagnostics, CJD, Parkinson's
format: 
  pdf:
    papersize: letter
    documentclass: article
    fontsize: 12pt
    geometry:
      - top=20mm
      - right=20mm
      - bottom=20mm
      - left=20mm
    fig-pos: "H"
    include-in-header: 
      - text: \usepackage{tabularray}
      - text: \usepackage{float}
      - text: \floatplacement{table}{H}
    html: default
mainfont: Calibri
bibliography: references.bib
bibliographystyle: apa
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(quicR)
library(dplyr)
library(tidyr)
library(kableExtra)
library(readxl)
library(readr)
library(ggplot2)
library(reshape2)
